---
title: "Homework 1"
author: "Anna Cook"
date: "9/17/2021"
output: pdf_document
---

### Number 1

400 / 50,001 = 0.0080
.8% chance of a MI in high risk men not on statins

### Number 2

240 / 50,002 = 0.0048
.48% chance of a MI in high risk men on statins

### Number 3

0.008 - 0.0048 = 0.0032

### Number 4

This difference in risk is very small, although the difference in risk is more than 1/3 the total risk for men not on statins, so this could be a significant difference? I'm not totally sure.

### Number 5

low risk, not on statins:
360 / 180,002 = 0.002

low risk, on statins:
30 / 20,001 = 0.0015

### Number 6

The difference for low risk men is only 0.0005, so this would make me think that statins do not really help much. 

### Number 7

(400 + 360) / (50,001 + 180,002) = 0.0033
.33% chance of MI in men not on statins

### Number 8

(240 + 30) / (50,002 + 20,001) = 0.0039
.39% chance of MI in men on statins

### Number 9

If we did not know about the risk status, we would probably conclude that statins have no effect on the chance of MI

### Number 10




```{r setup, include=FALSE}
library(readxl)
MI <- read_xlsx("MI_HW1.xlsx")

fit <- glm(MI ~ RiskScore + Statins, data = MI, family = binomial(link = "logit"))
```



```{r, include=FALSE}

```
